---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geodrawr

An interactive tool for making geo-spatial objects by clicks on the map  

## Installation  

You can install the released version from [GitHub](https://github.com/) with:


``` r
# install.packages("devtools")
devtools::install_github("Curycu/geodrawr")
```
## How to Use?

There are three draw tools : 

```{r example}
library(geodrawr)

# draw_polygons()
# draw_lines()
# draw_points()
```

#### case polygons  
  - click the map to make edges  
  - push Make button for polygon completion  
  - click the map to start to making an another polygon  
  - push Save button for save complete polygons as rds file  

#### case lines  
  - click the map to make edges  
  - push Cut button for line completion  
  - click the map to start to making an another line  
  - push Save button for save complete lines as rds file  
  
#### case points  
  - click the map to make points  
  - push Save button for save points as rds file
